%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hieu Do - Resume
% 7/26/2016
%
% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Chanchur Bansal}
{
\urlstyle{same}
	\faEnvelope \href{mailto:chanchurbansal@gmail.com}{ chanchurbansal@gmail.com}\\
	\faGithub \href{https://github.com/chanchurbansal}{ github.com/chanchurbansal}\\
	\faLinkedinSquare \href{https://www.linkedin.com/in/chanchurbansal/}{ linkedin.com/in/chanchurbansal}
    \faPhone { +91-7290017689}
    
}


    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.3\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection[Jaypee Institue of Information Technology]{Jaypee Institue of \\Information Technology}
\descript{Noida, Uttar Pradesh, India}
Bachelor of Technology in Computer Science \\
Expected Grad. June 2018 \\
Cum. GPA: 7.9\\
\sectionsep

\descript{Senior Secondary}
\subsection{Kulachi Hansraj Model School}
\descript{New Delhi, India}
Grad. May 2014  
\\ Percentage: 93.60
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\subsection[Languages]{Languages:}
C++, C, Python, JavaScript, Java, HTML, CSS, PHP, C++/CLI\\ 

\subsection[Frameworks]{Frameworks:}
Django \\

\subsection[Databases]{Databases:}
MongoDB, SQLite, MSSQL \\

\subsection[Tools]{Tools:}
Git, Android Studio, Adobe Photoshop CS6, Visual Studio \\ 

% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, Vietnamese\\
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     HACKATHONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Hackathons}
% HackMIT \textbullet{} hackNY \\
% WearHacks NY \textbullet{} Hackademics VN \\
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HANDLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Handles}
\subsection{CodeForces}
	\href{http://codeforces.com/profile/chanchurplay37}{codeforces.com/profile/\\chanchurplay37}\\
\subsection{CodeChef} \href{https://www.codechef.com/users/chanchurplay}{codechef.com/users/\\chanchurplay} \\
\subsection{HackerRank} \href{https://www.hackerrank.com/chanchurplay37}{hackerrank.com/\\chanchurplay37} \\
\subsection{HackerEarth} \href{https://www.hackerearth.com/@chanchurplay}{hackerearth.com/\\@chanchurplay} \\

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Coursework}
%Data Structure \\
%Algorithms \\
%Discrete Mathematics \\
%Artificial Intelligence \\
%Machine Learning \\
%Computer Architecture \\
%Computer Networking \\
%Operating Systems \\
%Object-Oriented Programming\\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Training
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Training}
Java Core Training Program\\
at DUCAT Institute, Noida \\
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% Dean's List\\
% NYU PROMISE Scholarship\\
% Shelby C. Davis Scholarship\\
% President’s Circle Scholarship\\
% \sectionsep

\sectionsep
%\DTMsetdatestyle{mylastupdate}
%\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Experience}

%\workplace{NYU IT – Application Infrastructure}{Jan 2016 – present}\\
%\position{Database Engineer Intern}{New York, NY}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Building a database management system to monitor all NYU data centers worldwide using SQL and Oracle APEX.
%\item Updating an internal server request tool by improving its user-interface and the service request process.
%\end{tightemize}
%\sectionsep





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}

\runsubsection{Advancements In Biometric Systems And Applications}
\descript{}
Published Research Paper on topic “Advancements In Biometric Systems And Applications” in “National conference on Advancement in Biometrics Trends and Its Applications (NCABTA - 2015)”	
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

\runsubsection{Navigation}
\descript{}
A Web application to get the optimal path (using A-Star) between source and destination searched from the list of places (using TRIE) or selecting a point on map using R-Tree.
\sectionsep

\runsubsection{Dr. Smart}
\descript{}
An intelligent android application (Material Design) that will predict the presence of a disease on basis of your current symptoms and medical results. Its Machine Learning algorithm is implemented in python.
\sectionsep

\runsubsection{Cricket Manager}
\descript{}
A utility software in C language, for an ongoing cricket league to keep record and analyze past matches.
\sectionsep 

\runsubsection{JIIT Medical}
\descript{}
A Database (MySQL) and Web Designing (PHP, CSS, and HTML) project to provide nearest medical assistance for patients.
\sectionsep

\runsubsection{Web Kiosk}
\descript{}
A college management software designed in C++% to facilitate students as well as teachers to view/update their complete record.
\sectionsep 

\runsubsection{8085 Simulator}
\descript{}
8085 microprocessor simulator in C++.
\sectionsep 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}

\vspace{0.5em} 
\begin{tightemize}

\item 84 World Rank in Round B, \customboldtext {Google KickStart}, 2017
\item 718 rank in round 2, \customboldtext {Facebook HackerCup}, 2017
\item Second Rank at IUPC, LNMIIT (Jaipur), 2017
\item Second prize in "AlgoFuzz 15.1", Inter College Programming Competition, JIIT, Sector - 128, Noida.
\item Runner up in Cyclotron, the science competition organized by Modern Public School in 2013.
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		Responsibilities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Responsibilities}

\vspace{0.5em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Problem Setter at Knuth-Cup (Intercollegiate coding contest)
\item Core Team Member at Knuth Programming Hub, JIIT-62 and organized many contests and workshops.
\item Volunteer at Igniting Young Mind, An NGO at Vijay Nagar, Delhi to teach unprivileged students.
\item 	Member of Robotics club in college
\end{tightemize}
\sectionsep



\end{minipage} 

\end{document}  
